The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-04 writing/draft3/draft4.tex
write more

	In order to obtain a conformable dataset of yield, precipitation and temperature (that is all data should have same frequency and spatial resolution), the gridded weather data were first averaged over the counties of Kenya so that we obtained daily time series of each county. In the next step, we aggregated the resulting county level time series temporally to obtain yearly time series corresponding to the frequency of the yield data. We only considered weather data during the rainy seasons which we defined as follows, using the classification of...

\color{blue}
\begin{itemize}
\item Source of the climate data: BOKU and Berkeley Earth
\item Source of the yield data (Kenya MoA)
\end{itemize}

\color{black}
\subsection{Statistical approach}

>>>>

	In order to proceed with the analysis, the daily weather data had to be converted to an yearly, county-level panel to correspond with the yield data. The first step of this procedure was averaging the gridded weather data over the counties of Kenya resulting in daily time series for each county. In the next step, we aggregated the resulting county level time series temporally to obtain yearly time series. We only considered weather data during the rainy seasons which we defined as follows, using the classification of...

\subsection{Statistical approach}
